### 2022-11-29 response-reviewers/response-reviewers.tex

\vspace{.3cm}

We would like to thank Reviewer 1 for her/his helpful comments and suggestions.

\section*{Reviewer 2 Comments and Responses}

\textbf{Major issues:}

\noindent \textbf{1)} Reviewer 2 writes: ``I believe the main framing of this manuscript should focus on explaining the interesting variation between studies (i.e., when do the law of 1/n or the reverse law are expected). From this perspective, the introduction part of the paper currently quickly jumps to the technicalities of the meta-analysis (e.g., a description of the two models used, measurement of DV etc.; see p. 2). These technical descriptions should appear in the method section. Instead, it would be more helpful to see some theoretical discussion on the reasons the literature proposes for the heterogeneity found in this study - even in a concise manner.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that the technical discussion in the introductory section was misplaced. We have restructured the Introduction to fit Reviewer 1 and Reviewer 2's recommendations. As displayed above (p.4 of this letter), we expanded the literature review to capture the main points in the debate that dialogue with our findings. We have also made our critiques of the scholarship more clear, explicitly pointing to which we thought were the sources of heterogeneity in previous work in the Discussion section. Moreover, in Section A of the Supplementary Materials, we added a brief discussion of the theory developed by \citet{weingast1981political}, and also the "reverse law of $1/n$" by \citet{primo2008distributive}. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{2.1)} Reviewer 2 writes: ``It is currently difficult to understand why many studies included in the meta-analysis have several effect sizes. Is it because of using different dependent? Some examples would help the readers.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    In our restricted sample, a study can supply more than one coefficient if it employs more than one dependent or independent variable. Studies that analyse bicameral systems use upper chamber size and lower chamber size as independent variables, and thus supply two coefficients each. These studies are \citet{chen2007law, crowley2019law, gilligan2001fiscal, lee2015supermajority, lee2016supermajority, lee2018court, maldonado2013legislatures, ricciuti2003trading, ricciuti2004legislatures, primo2006stop}. The paper by \citet{bradbury2001legislative} alone supplies four coefficients, as they use two independent variables (upper chamber size and lower chamber size) and two dependent variables (expenditure as share of the GDP and per capita expenditure). Two other papers \citep{bjedov2014impact, erler2007termlimits} also use both of these dependent variables and only one independent (lower chamber size), supplying two coefficients each.

    To the extended sample, each paper can supply several coefficients because studies usually submit their data to a series of models where they include or exclude different controls or interaction terms, or perform slightly different tests. For instance, we drew twelve coefficients from \citet{fiorino2007legislature}. From a single table (Table 4) in their paper, we extracted four coefficients for the same variable combination (lower chamber size and per capita expenditure).
\end{quote}

\vspace{.3cm}

\noindent \textbf{2.2)} Reviewer 2 writes: ``Moreover, and more substantially, I am not sure how including studies with several effect sizes in a separate model (p. 7) can solve the violation of non-independent effect sizes, required in meta-analyses. The authors do not report the statistical models they used for solving these violations (I did not find it in the appendix either). There are various ways to address such issues, such as robust variance estimation (see Hedges et al., 2010) or using multi-level meta-analyses (see e.g. application in Matthes et al., 2019).

Furthermore, since there were several studies focusing on the same country (e.g., 14 studies investigating the US), did they use the same samples in their analysis? If so, doesn't it violate the non-independence assumption on its own (as they use the same district ``sample'')? If that is the case, the authors should treat this effect size dependency also for the first model (with the 42 main coefficients). These issues are very important since some of the authors' findings are based only on the ``extended models'' in Table 3 (i.e., those including 142 effect sizes, even from studies reporting several effect sizes related to the same sample). If these findings are based on biased estimates, we should be a lot more cautious interpreting them.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    As Reviewer 2 correctly notes, the coefficient extraction procedure we just presented in the previous response is the main source of effect size dependence in our extended sample analyses. An additional source of dependence is the fact that many studies analyse the same cases, sometimes even using the same data sources. The Reviewer is also correct to point out that separating the effect sizes into a restricted and an extended sample does not properly address the dependence of the coefficients within the extended sample. We followed the Reviewer's suggestion rigorously by employing multilevel random effect models \citep{cheung2014modeling, matthes2019meta} in all of our estimations. A thorough explanation of how we identified, grouped the studies that constitute the new levels, and coded them can be found in section H.1 of the Supplementary Materials. We describe the procedure more succinctly in the Data and Methods section in the main paper (last paragraph on page 7):

    ``\textit{We add two extra levels to the regular meta-analysis, one including a unique publication ID for each paper, and another indicating the data source used in the original study. By adding these two levels, we account for within- and between-study variation, thus removing these sources of effect size dependency and improving the accuracy of the results.}''

    We believe the inclusion of additional levels reduces the bias previously present in our analyses, producing far more reliable estimates. We are highly appreciative of this comment, as it has ignited major changes in our manuscript, severely improving the robustness of our results. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} Reviewer 2 writes: ``How did the authors convert the original studies' coefficients into standardized effect sizes? It is important to mention how the authors render these coefficients comparable due to the various research designs included in the meta-analysis.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have included a paragraph in the Data and Methods section (p.7) to clarify the coefficient standardisation procedure. It reads:

    ``\textit{We use Hedges' $g$ to calculate effect sizes in our meta-analysis \citep{hedges1981distribution}. While there are other methods to standardise coefficients in meta-analytic studies, Hedges' $g$ corrects for upward bias in small sample sizes and is considered more robust than measures such as Cohen's $d$ \citep{lakens2013calculating}. We estimate the Standardised Mean Difference (SMD), which represents the effect size in each study relative to the variability observed in that study, by extracting the coefficients and the standard errors from all articles included in our sample and converting them to Hedges' $g$. In cases where authors did not report the standard errors for their estimates, we computed them using the t-statistic presented in the original tables.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{4)} Reviewer 2 writes: ``our results suggest that study coefficients are highly sensitive to research design choices'' (p. 13) - this is a rather bold statement (``highly sensitive'') since most differences between study designs are nonsignificant (on Table 3). I would tone down this argument much more and address its limitations in the discussion.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have adapted the language when referring to the effects of estimation methods according to the Reviewer's suggestions throughout the paper. For instance, paragraph 6 of the Introduction (p.3) reads:

    ``\textit{However, when we look only at articles that employ regression discontinuity designs, we see that all four papers included in our sample suggest that a higher number of legislators leads to lower public spending \citep{debenedetto2018effect, hohmann2017effect, lewis2019legislature, petterssonlidbom2012size}. In this regard, it is possible that methodological choices partially explain the divergent results observed in the literature, as studies that use causal inference methods consistently point to the same direction. One limitation of this finding is that these studies only test the impact of lower house size on the natural logarithm of expenditure per capita, thus it remains unclear whether the results hold with other variables.}''

    The Results and Discussion sections present these findings more objectively. On page 14, we report the following conclusion regarding estimation methods: ``\textit{The meta-regressions confirm that modern estimation methods such as RDDs and panel/fixed-effects models decrease effects more frequently than OLS regressions.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{5)} Reviewer 2 writes: ``I encourage the authors to elaborate more on the implications of their results rather than to simply describe them, especially in the context of their moderators (electoral systems and possibly, the research design - but see my above concerns regarding the results related to study designs). Although the format should be concise, such a discussion will improve the readers' understanding of the main findings much more (especially non-expert readers). For example, the seemingly "methodological" explanation of research design as a moderator has substantial implications. If that is the case, to what extent can we lean on earlier studies that did not use causal inference?''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    Following Reviewer 2's recommendations, we have more appropriately framed the paper so that we discuss the institutional moderators and their relationship to the theory across the entire piece. Since we changed our model specifications and added a new moderator, our Results section was also significantly altered. We reduced the Meta-Analysis subsection (3.2) and expanded the Meta-Regressions subsection (3.3) to account for the most relevant and auspicious findings. In this sense, in paragraph 2 of subsection 3.3, we explain to the reader how she should interpret the meta-regression results. We believe this makes our arguments about the meta-regression results more compelling. We also added more substantive insights to accompany the description of meta-regression results in each paragraph of section 3.3.

    We present and partly interpret our results in the Introduction section, reporting back to elements from the literature and to the theory. The last paragraph in the Introduction (p.3) reads:

    ``\textit{The meta-regressions provide additional evidence that our study sample is highly heterogeneous and that effect sizes differ substantially according to study specifications. When using an extended sample of 162 coefficients, we find that unicameralism is associated with higher public spending, as predicted by the ``law of $1/n$''. Since most unicameral legislatures in our sample are local governments (municipalities or districts), this result supports the predictions of \citet{weingast1981political}. Moreover, our meta-regressions indicate that larger upper chambers spend more in terms of per capita expenditure than lower chambers, a result that also appears in the binomial tests. Overall, non-majoritarian voting systems seem to decrease government spending, following the idea that the $1/n$ effect grows weaker as the empirical cases distance from the original definition of the law. Finally, meta-regression results confirm that regression discontinuity designs reduce public spending estimates.}''

    The Discussion section has also increased both in size and scope. Now, we more aptly establish the dialogue between our electoral system findings and the original theory and literature. For instance, in page 15, the following reads:

    ``\textit{While we believe that moving beyond the majoritarian districts framework could produce valuable insights, institutional features that are central to the theory cannot be overrun. For example, proportional representation (PR) electoral systems allow candidates whose constituents are spread across large territories to provide diffused public goods and win elections. However, geographically-targeted service provision is at the very core of the legislative behaviour that produces the "law of $1/n$". Thus, scholars should consider the possible implications of these micro-level dynamics when applying the "law of $1/n$" logic to different settings.}''
\end{quote}

\vspace{.3cm}

\noindent \textbf{More minor comments:}

\vspace{.3cm}

\noindent \textbf{1)} Reviewer 2 writes: ``Table 1 - it will be clearer to separate the notes at the bottom of the table into separate columns. For instance, note \#1 will explain the abbreviations of the Journal column note \#2 will refer to the Country column. Otherwise, the reader has to manually look for a given abbreviation out of the rather long list.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree this can be an unnecessary inconvenience to the reader. We have changed the notes in Table 1 according to the Reviewer's specifications. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} Reviewer 2 writes: ``Also regarding Table 1, I believe it will be more convenient to simply write the authors and the year of publication in the first column (e.g., "Stein et al., 1998") while keeping the table order as it is (according to the year of publication) - rather than splitting them into two columns. I am also not sure whether the title of the paper really helps the readers or simply confuses them (it makes the table less elegant in my opinion). I would delete the title (if a reader wishes to see the full reference, she can look it in the bibliography). In contrast, it will be more beneficial to mention inside the table the DVs used in each study (as currently explained in the body text; p. 6).''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We have made these alterations to Table 1 accordingly. We also added a column for the new Institutional Design moderator.
\end{quote}

\vspace{.3cm}

\noindent \textbf{3)} Reviewer 2 writes: ``The use of $n$ and $k$ as signifiers of the independent variables is a bit confusing throughout the paper since in the meta-analyses domain, they usually signify the number of effect sizes ($k$) and the number of respondents per study ($n$). More broadly, it is even more confusing when discussing Table 3 (the reader has to remember what $n$ and $k$ represent, instead of simply writing the meanings) or when interpreting its results in the discussion part.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We agree that adding labels to variables is an unnecessary inconvenience to the reader. All references to the independent variables now translate their full meaning.
\end{quote}

\vspace{.3cm}

\noindent \textbf{4)} Reviewer 2 writes: ``I appreciate the authors' elaborated appendix, but the readers might get a bit lost without specific references to the sub-sections in it throughout the main paper: for example, not just referring to the Supplementary Materials in general, but to the specific section in it. Moreover, the authors should consider leaving out the R code from the online appendix, and simply anonymously upload it to an external open science source. For people who are not experts in R (and perhaps also for those who are), the combination of code and text can be a bit confusing.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    As noted above, we agree that only a handful of scholars would be interested in R scripts, which get in the way of most readers. We have split the Supplementary Materials into two documents. The one we refer to as the ``Supplementary Materials'' includes a discussion of the theory, the study selection procedures, a description of how we treated the data in detail, and analysis results. The other collects all the R code we wrote for each stage of data collection and analysis. We recommend the latter is used by those wishing to replicate our work and strongly encourage peers to use it and produce new meta-analyses in the social sciences.
\end{quote}

\vspace{.3cm}

\noindent \textbf{5)} Reviewer 2 writes: ``To facilitate interpretation of Figure 1, it would be more convenient to number each plot, and refer to it in the body text (pp. 10-11).''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    All plots in Figures 1 and 2 are now individually numbered, and referred to in the body text.
\end{quote}

We would like to thank Reviewer 2 for her/his helpful comments and suggestions.

\section*{Reviewer 3 Comments and Responses}

\noindent \textbf{1)} Reviewer 3 writes: ``First, I am concerned about the first criterion for inclusion in the meta-analysis. Studies could only be included if they cited the Weingast et al. (1981) study. While I don't doubt that this work is foundational to the distributive politics literature, it is an unnecessary restriction. Are there any studies that fit the other two inclusion criteria but do NOT cite Weingast? Maybe there aren't any, but if there are, they should be included since they are still just as relevant to the question at hand. The second inclusion criterion is the most important: a study that quantitatively analyzes the variables of interest. This of course makes the literature search more difficult, but also more comprehensive, which is a main benefit of good meta-analyses.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    The concern Reviewer 3 expresses is one we share. We address this comment by conducing a second round of record collection. We increased our breadth by using a search string with key terms on Google Scholar. We meant to capture all articles that approached the relationship between legislature size and public spending. The search string we used is the following:

    \texttt{\justify ("upper chamber size" OR "lower chamber size" OR "council size" OR "parliament size" OR "legislature size" OR "number of legislators" OR "legislative size") AND ("spending" OR "expenditure" OR "government size")}

    We fuzzy matched the resulting database with the one we had originally analysed to remove all entries we had already covered. As part of this eligibility analysis, we assessed an additional 3,042 records. The exclusion criteria and procedures were the exact same as those performed in the first round (for the original manuscript the Reviewers and Editors read). They are fully detailed in Sections B and C of the Supplementary Materials. The full dataset of excluded records is available for online consultation in the article's GitHub repository.

    Resulting from this second round of surveying the literature, we found two articles that satisfied all the criteria. They were thus included in our analysis. The new papers are \citet{coate2011government} and \citet{debenedetto2018effect}. We thank Reviewer 3 for this comment, as it has effectively made our survey more comprehensive. 
\end{quote}

\vspace{.3cm}

\noindent \textbf{2)} Reviewer 3 writes: ``Second, another main benefit of meta-analyses is to assess the possibility of publication bias. Studies are often more likely to be published if they find statistically significant effects in the direction that is expected, but a comprehensive search of ongoing studies allows meta-analysts to check this. In the current sample, only 4 papers are unpublished, but I also wonder if this is due to the restricted inclusion criteria. For example, if one uses the Google Scholar feature to find articles citing Weingast et al, that would only pick up papers that are already published in a journal or otherwise online, but it may miss any working papers that are not shared publicly. A more comprehensive search may result in more unpublished studies. Either way, can the authors include some sort of formal tests or visualizations for publication bias, such as funnel plots? I think if these two revisions could be made this paper would make a strong contribution.''

\vspace{.3cm}

\noindent \textbf{Response:} 
\begin{quote}
    We understand the Reviewer's concern with publication bias, and we accept both of her/his suggestions in this comment. First, so as not to miss any papers that have not been circulated as Working Papers, we seek after those that have been shared as ongoing projects. We looked into the personal webpages of the scholars who wrote all of the papers in our original sample of studies. In their personal platforms, we scouted for pieces of research about distributive politics. We targeted specifically those that had not been uploaded to large repositories and open archives such as SocArXiv, as those tend to appear in Google Scholar searches. We gathered 15 pieces of work with titles potentially related to our research topic and submitted them to the eligibility criteria. None of these papers were included in the final sample. This procedure is also explained in Section B of the Supplementary Materials, and a dataset displaying all records assessed and their reason for exclusion is available for online consultation as well.

    Attending to the Reviewer's second request, we add \citet{egger1997bias} funnel plots to assess publication bias in all of our meta-analyses. Funnel plots display the possibility of having a file-drawer effect, meaning they can indicate whether null results are under-represented in our sample or not. The funnel plots are available in the Supplementary Materials below the forest plot for each variable combination in the restricted and in the extended samples (Sections H and I). All but one of our \citet{egger1997bias} tests reject the hypothesis of publication bias.
\end{quote}

We would like to thank Reviewer 3 for her/his helpful comments and suggestions.

\newpage
\bibliography{references.bib}
\bibliographystyle{apalike}

\end{document}d
